Detailed Geant4 simulations of the ANITA and ANITA-CUP neutron facilities

### 2015-04-20 Paper2015.tex
Spell check.

Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
As CUP is upstream of the collimator the distribution is not not circularly symmetric.
In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
The present results underestimate measurements at the CUP by 28\%.
\todo{Check CUP fluence rates.}

@@

Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP consists of three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
The present simulations confirm the Prokofiev et al. semi-empirical multicomponent model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.

@@

\section{Conclusion}
We have used Geant4 for detailed Monte Carlo simulations of the ANITA and ANITA-CUP neutron SEE test facilities at The Svedberg Laboratory.
Neutron fluence rate, energy spectrum, time profile and and spatial distribution show good agreement with measurements and independent simulations (using MCNPX).
Gamma radiation characteristics have also been predicted and preliminary evaluations indicate that they are consistent with a limited set of measurement data.
For reasons of space only a small subset of results are presented here.
Evaluation of our results is still in progress; additional data and evaluation will be presented in our final paper.

>>>>

Fig.~\ref{fig:CUPDensity} shows the spatial distribution of neutrons above \SI{10}{\MeV} at the CUP.
As CUP is upstream of the collimator the distribution is not circularly symmetric.
In the central region the calculated neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{215}{\nA} is \SI{8.44e6}{\neutron\per\cm\squared\per\second}, compared to \SI{1.17e7}{\neutron\per\cm\squared\per\second} from measurements~\cite{Prokofiev2014}.
The present results underestimate measurements at the CUP by 28\%.
\todo{Check CUP fluence rates.}

@@

Prokofiev et al.~\cite{Prokofiev2014} note that the TOF spectrum at the CUP consists of three parts, a component directly from the target, one scattered forward from target surroundings, and one scattered backwards from the front face of the collimator block.
The present simulations confirm the Prokofiev et al. semi-empirical multi-component model. Details of this confirmation will be presented in the full paper but are omitted here for brevity.

@@

\section{Conclusion}
We have used Geant4 for detailed Monte Carlo simulations of the ANITA and ANITA-CUP neutron SEE test facilities at The Svedberg Laboratory.
Neutron fluence rate, energy spectrum, time profile and spatial distribution show good agreement with measurements and independent simulations (using MCNPX).
Gamma radiation characteristics have also been predicted and preliminary evaluations indicate that they are consistent with a limited set of measurement data.
For reasons of space only a small subset of results are presented here.
Evaluation of our results is still in progress; additional data and evaluation will be presented in our final paper.
